Drawing Trees and Animating Tree Changes

### 2010-03-08 presentation/talk.tex
Modifications to the talk.

\documentclass{beamer}
\usetheme{manhattan}  % Now it's a beamer presentation with the UO theme!

@@

\fst{The Problem}{
\begin{itemize}
\item Trees undergoing changes occur in many contexts
    \begin{itemize}
        \item Visualization can be a help 
    \end{itemize}
\item Writing graphics and layout code from the ground up is hard.
\item Writing animation code is harder
\item Worst of all often the people who have skills with algorithms have little 
  experience with graphics programming.
    \begin{itemize}
        \item And visa-versa
    \end{itemize}
\end{itemize}
}

@@

@@

\section{Wrap-Up}

>>>>

\documentclass{beamer}
\usetheme{manhattan}  % Now it's a beamer presentation with the Manhattan College theme!

@@

\fst{The Problem}{
\begin{itemize}
\item Trees undergoing changes occur in many contexts
    \begin{itemize}
        \item Visualization can be a help 
    \end{itemize}
\item Writing graphics and layout code from the ground up is hard.
\item Writing animation code is harder
\item Worst of all often the people who have skills with algorithms have little 
  experience with graphics programming.
    \begin{itemize}
        \item And vice-versa
    \end{itemize}
\end{itemize}
}

@@

\fst{How It Works}{
    \begin{itemize} 
        \item Each vertex is a magnet that repulses its neighbors
        \item Each edge is a spring, pulling adjacent vertices closer
        \item Each vertex has a fixed vertical position and a fixed horizontal order
    \end{itemize} 
}

@@

\section{Wrapping Up}
